---
output:
  md_document:
    variant: gfm
html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


# tidytree: A Tidy Tool for Phylogenetic Tree Data Manipulation

```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/tidytree?color=green)](https://cran.r-project.org/package=tidytree)
`r badge_devel("guangchuangyu/tidytree", "green")`
[![](https://cranlogs.r-pkg.org/badges/grand-total/tidytree?color=green)](https://cran.r-project.org/package=tidytree)
[![](https://cranlogs.r-pkg.org/badges/tidytree?color=green)](https://cranlogs.r-pkg.org/downloads/total/last-month/tidytree)
[![](https://cranlogs.r-pkg.org/badges/last-week/tidytree?color=green)](https://cranlogs.r-pkg.org/downloads/total/last-week/tidytree)


```{r comment="", echo=FALSE, results='asis'}
cat(packageDescription('tidytree')$Description)
```

Visit <https://yulab-smu.top/treedata-book/> for details.


## :writing_hand: Author

Guangchuang YU

School of Basic Medical Sciences, Southern Medical University

<https://guangchuangyu.github.io>

[![saythanks](https://img.shields.io/badge/say-thanks-ff69b4.svg)](https://saythanks.io/to/GuangchuangYu)
`r badger::badge_custom("follow me on", "WeChat", "green", "https://guangchuangyu.github.io/blog_images/biobabble.jpg")`



## :arrow_double_down: Installation

Get the released version from CRAN:

```r
install.packages("tidytree")
```

Or the development version from github:

```r
remotes::install_github("GuangchuangYu/tidytree")
```

## :sparkling_heart: Contributing

We welcome any contributions! By participating in this project you agree to
abide by the terms outlined in the [Contributor Code of Conduct](CONDUCT.md).

