---
output:
  md_document:
    variant: gfm
html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


# tidytree: A Tidy Tool for Phylogenetic Tree Data Manipulation

```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/tidytree?color=green)](https://cran.r-project.org/package=tidytree)
`r badge_devel("guangchuangyu/tidytree", "green")`
![](https://cranlogs.r-pkg.org/badges/grand-total/tidytree?color=green)
![](https://cranlogs.r-pkg.org/badges/tidytree?color=green)
![](https://cranlogs.r-pkg.org/badges/last-week/tidytree?color=green)


```{r comment="", echo=FALSE, results='asis'}
cat(packageDescription('tidytree')$Description)
```


## Authors

Guangchuang YU

School of Basic Medical Sciences, Southern Medical University

<https://guangchuangyu.github.io>

[![saythanks](https://img.shields.io/badge/say-thanks-ff69b4.svg)](https://saythanks.io/to/GuangchuangYu)
`r badger::badge_custom("follow me on", "微信", "green", "https://guangchuangyu.github.io/blog_images/biobabble.jpg")`
`r badger::badge_custom("打赏", "支付宝/微信", "green", "https://guangchuangyu.github.io/blog_images/pay_qrcode.png")`


## Installation

Get the released version from CRAN:

```r
install.packages("tidytree")
```

Or the development version from github:

```r
## install.packages("devtools")
devtools::install_github("GuangchuangYu/tidytree")
```

