---
title: "tidytree: A Tidy Tool for Phylogenetic Tree Data Manipulation"
author: "Guangchuang Yu\\

        School of Public Health, The University of Hong Kong"
date: "`r Sys.Date()`"
csl: nature.csl
output:
  prettydoc::html_pretty:
    toc: true
    theme: cayman
    highlight: github
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{tidytree introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r style, echo=FALSE, results="asis", message=FALSE}
knitr::opts_chunk$set(tidy = FALSE,
		   message = FALSE)
```


```{r echo=FALSE, results="hide", message=FALSE}
library("ape")
library("treeio")
library("tidytree")
```



# Convert tree to tidy data frame (tree_tbl object)

## phylo object

```{r}
library(ape)

tree <- rtree(4)
tree
x <- as_data_frame(tree)
x
```

## treedata object

```{r}
library(treeio)

file <- system.file("extdata/BEAST", "beast_mcc.tree", package="treeio")
beast <- read.beast(file)
beast
y <- as_data_frame(beast)
y
```

# Convert tree_tbl object to a tree object

```{r}
as.phylo(x)
as.treedata(y)
```

# Access related nodes

`dplyr` verbs can be applied to `tree_tbl` directly to manipulate tree data. In
addition, `tidytree` provides several verbs to filter related nodes, including
`child`, `parent`, `offspring`, `ancestor` and `sibling`.

These verbs accept a `tree_tbl` and selected node which can be node number of label.


```{r}
child(y, 23)
parent(y, 23)
offspring(y, 23)
ancestor(y, 23)
sibling(y, 23)
```

